Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-08 ms.tex
Modify Section 4
From 38453eb:
============

In ms.tex,

(*) Modify Section 4

Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling \citep{thy15} with no thermal noise fluctuations (bottom), for reference. The dynamic range (in power spectrum units) in the averaged data (middle) is a factor $\gtrsim 10$ higher relative to that in a single snapshot (top) similar to the one used in \citet{thy15}, and is consistent with the improvement expected from averaging 12 independent snapshots. With this improvement in sensitivity, the foreground power near the horizon limits (white dotted lines) has become $\gtrsim 10$ times more prominent. We now note that faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which is not seen in the single snapshot, thus confirming effective lowering of thermal fluctuations. We identify these faint features as the response in delay space of the MWA coarse band edges flagged periodically every 1.28~MHz.

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{multi_baseline_CLEAN_fhd_avg_visibilities_amplitudes_185.0_MHz_30.7_MHz.eps}
\includegraphics[width=\linewidth]{multi_baseline_fhd_sim_visibilities_amplitudes_comparison_185.0_MHz_30.7_MHz.eps}
\caption{Delay power spectra obtained from a single snapshot ({\it top}), by averaging 12 snapshots of LST aligned MWA data ({\it middle}), and from modeling with no thermal noise added ({\it bottom}) shown for reference. The $x$-axis, denoted by $|\boldsymbol{b}|$ (and $k_\perp$), represents angular (and spatial) scales in the plane of the sky while the $y$-axis, shown in $\tau$ and $k_\parallel$, denotes the spatial scales along the line of sight. White dotted lines are the horizon delay limits. Dynamic range in the delay power spectra of MWA data has increased by a factor $\sim 10$ after averaging (middle) relative to that in a single snapshot (top). Power near the horizon limits caused by wide-field effects are prominent. Faint horizontal features at $\tau=\pm 0.78\,\mu$s are visible due to effective lowering of thermal fluctuations and are the response to periodic coarse band edge flagging of MWA data every 1.28~MHz. \label{fig:delay-spectra}}
\end{figure}

@@

The delay power spectra morphologies from data and modeling are remarkably similar despite some differences in the amplitude scales. We attribute these differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in \citet{thy15}.

We focus on the peaks near the horizon limits in the data. Typically, the power near the negative horizon limit is seen with a signal-noise ratio (SNR) $\sim$~10-100, while that around the positive horizon limit is $\sim$~100-1000. The models of \citet{thy15} have noted that the foreground power near the horizon limits is due to the nature of wide-field measurements, and is predominantly composed of diffuse emission especially on baseline lengths $\lesssim 100$~m. Based on the morphological agreement between the data and the models, we conclude the features noted in our current analysis are a robust detection of the {\it pitchfork} signature predicted in \citet{thy15}.

>>>>

Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling (bottom) with no thermal noise fluctuations \citep{thy15}, for reference. In all panels, the {\it foreground wedge} bounded by horizon limits (white dotted lines) is prominent. The bright branch of power at $\tau=0$ corresponds to foreground emission from the main lobe of the power pattern pointed at the zenith.

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{multi_baseline_CLEAN_fhd_avg_visibilities_amplitudes_185.0_MHz_30.7_MHz.eps}
\includegraphics[width=\linewidth]{multi_baseline_fhd_sim_visibilities_amplitudes_comparison_185.0_MHz_30.7_MHz.eps}
\caption{Delay power spectra obtained from a single snapshot ({\it top}), by averaging 12 snapshots of LST aligned MWA data ({\it middle}), and from modeling with no thermal noise added ({\it bottom}). The $x$-axis, denoted by $|\boldsymbol{b}|$ (and $k_\perp$), represents angular (and spatial) scales in the plane of the sky while the $y$-axis, shown in $\tau$ and $k_\parallel$, denotes the spatial scales along the line of sight. White dotted lines are the horizon delay limits. Dynamic range in the delay power spectra of MWA data has increased by a factor $\sim 10$ after averaging (middle) relative to that in a single snapshot (top). Power near the horizon limits caused by wide-field effects are prominent. Faint horizontal features at $\tau=\pm 0.78\,\mu$s are visible due to effective lowering of thermal fluctuations and are the response to periodic coarse band edge flagging of MWA data every 1.28~MHz. \label{fig:delay-spectra}}
\end{figure}

The key defining feature of the {\it pitchfork} signature is an enhancement in foreground power near the horizon limits. In the individual snapshot, similar to the one used in our original study, faint features are visible near the horizon limits. But the high level of thermal fluctuations makes their significance marginal. In contrast, the dynamic range (in power spectrum units) in the averaged data (middle) is a factor $\gtrsim 10$ higher relative to that in a single snapshot (top), and is consistent with the improvement expected from averaging 12 independent snapshots. With this improvement in sensitivity, the foreground power near the horizon limits (white dotted lines) appears $\gtrsim 10$ times more prominent. We now note that faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which is not seen in the single snapshot, thus confirming effective lowering of thermal fluctuations. We identify these faint features as the response in delay space of the MWA coarse band edges flagged periodically every 1.28~MHz.

@@

The delay power spectra morphologies from data and modeling are remarkably similar in broad shape although they exhibit some differences in the amplitude scales. We attribute these differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in \citet{thy15}.

We focus on the peaks near the horizon limits in the data. Typically, the power near the negative horizon limit is seen with a signal-noise ratio (SNR) $\sim$~10-100, while that around the positive horizon limit is $\sim$~100-1000. % The models of \citet{thy15} have noted that the foreground power near the horizon limits is due to the nature of wide-field measurements, and is predominantly composed of diffuse emission especially on baseline lengths $\lesssim 100$~m. 
Based on the morphological agreement between the data and the models, we conclude the features noted in our current analysis are a robust detection of the {\it pitchfork} signature predicted in our earlier study.
